Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-09-26 RR_manuscript/Draft_RR.Rmd
typos and stuff

In this article, we investigate the impact of analytic choices on research results when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the *operationalization* of a complex signal and decisions regarding *statistical analysis*.
Specifically, we discuss the degree of variability in research results obtained by 30 teams who had to choose the operationalization and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
Our goals are twofold: (i) our study conceptually replicates previous many-analyses projects, by probing the effects of different statistical analyses and by assessing the generalizability of published findings to other disciplines (here, the speech sciences);
(ii) our study extends the scope of inquiry to include flexibility in the operationalization of complex human behavior (here, human speech).
This is an important addition in that the increased number of "forking paths" in the "garden of analytic choices", deriving from the many decisions involved in quantification, might reveal a higher degree of variability across analysts than what previously observed, thus giving us a more realistic estimate of variability across analysts.

@@

Consequently, it is likely that a good part of published papers present overconfident interpretations of data and statistical results based on idiosyncratic analytic strategies [e.g., @simmons2011false; @gelman2014statistical].
These interpretations, and the conclusions that derive from them, are thus associated with an unknown degree of uncertainty (dependent on the strength of evidence provided) and with an unknown degree of generalizability (dependent on the chosen analysis).
Moreover, the same data could lead to very different conclusions depending on the analytic path taken by the researcher.
However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
Despite recent efforts to improve transparency and reproducibility [e.g. @miguel2014promoting; @klein2018practical] and the advent of freely available and accessible infrastructures, such as those provided by the Open Science Framework (osf.io), critical re-analyses of published analytic strategies are still uncommon because data sharing remains rare [@wicherts2006poor].

@@

Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
In a seminal collaborative effort, @silberzahn2018many let twenty-nine independent analysis teams address the same research hypothesis.
Analytic approaches and consequently the results varied widely between teams.
Sixty-nine percent of the teams found support for the hypothesis, and 31% did not.
Out of the 29 analytic strategies, there were 21 unique combinations of covariates.
Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses.

The authors results suggest that analytic plurality may be an inevitable byproduct of the scientific process and not necessarily driven by different levels of expertise or bias.

Several other recent studies corroborated this analytic flexibility across different disciplines.
@dutilh2019 and @starns2019assessing investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams (see also @Parker2020 on analytic flexibility in ecology, and @botvinik-nezer2020 on neuroimaging data).
@bastiaansen2020 crowdsourced clinical recommendations based on analyses of an individual patient.
Their results suggests that analysts differed substantially regarding decisions related to both the statistical analysis of the data and the theoretical rationale behind interpreting the statistical results.

Extending on the many-analysts approach, @landy2020crowdsourcing asked 15 research teams to independently design studies to answer the same research questions.
Again, they found vast heterogeneity in researchers' conclusions which was not predicted by the researchers' expertise but seem to be more dependent on the research question itself.
This is in line with a recent re-analysis of @silberzahn2018many by @auspurg2021has.
The authors argue that the observed heterogeneity across analysts in @silberzahn2018many might have been driven by flexibility in statistically interpreting the research question.

While these studies attested a large degree of analytic flexibility with possibly impactful consequences, they focused on analytic decisions related to statistical inference or the architecture of computational models. 
In these studies the data sets were fixed and neither data collection nor measurement could be changed.
Thus the estimates of variability found in the literature might reflect a lower bound only, ignoring large parts of the forking path related to measurement.

However, in many fields the primary raw data are complex signals that need to be operationalized relative to a theoretically motivated research question.
This is especially true in the social sciences, where the phenomenon under investigation corresponds to both observable and unobservable human behavior.

@@

Depending on the speaker's intention, this sentence can be said in different ways.
For instance, if the speaker is exhausted by all their meetings, they might acoustically highlight the word *another* or *meeting* to contrast it with more pleasant activities.
If, on the other hand, the speaker is just tired of video conferences, as opposed to say face-to-face meetings, they might acoustically highlight the word *Zoom*.

@@

From a phonetic viewpoint, linguistically relevant units are inherently multidimensional and dynamic: they consist of clusters of parameters that are modulated over time.
The acoustic parameters of units are usually asynchronous, i.e. they appear at different time points in the unfolding signal, and overlap with parameters of other units [e.g. @jongman2000acoustic; @lisker1986voicing; @summerfield1981articulatory; @winter2014spoken].
A classical example is the distinction between voiced and voiceless stops in English (i.e. /b/ and /p/ in *bear* vs *pear*).
This contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds [@lisker1977rapid].
Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
For example, the initial /l/ of the English words *led* and *let* is affected by the voicing of the final consonant (/d, t/) [@hawkins2004influence].

The multiplicity of phonetic measurements grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
For example, studies investigating acoustic correlates of word stress (e.g. the difference between *ínsight* and *incíte*) use a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) [e.g., @gordon2017acoustic].
Moving on to the expression of higher-level communicative functions, like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances [e.g., @ladd2008intonational].
Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions [e.g., @niebuhr2011].
The latter can also be expressed by global vs local pitch modulations [@heuven2002], as well as acoustic information within the temporal or spectral domain [e.g., @van2005speech].
Extra-linguistic information, like the speaker's intentions, levels of emotional arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch [@foulkes2006; @ogden2004; @white2009].

In short, when testing hypotheses on speakers' intentions with speech production data, researchers are faced with many choices and possibilities.
The larger the functional domain (e.g. segments vs words vs utterances), the higher the number of conceivable operationalizations.
For example, several decisions have to be made when comparing the two realizations of the sentence in (1), one of which is intended to signal emphasis on *another* and one of which emphasizes *Zoom* (see 2a and 2b).

@@

Do we compare only the word *another* in (2a) and (2b), or also the word *Zoom*?
Do we measure utterance-wide acoustic profiles, whole words, or just stressed syllables?
Do we average across the chosen time domain or do we measure a specific point in time?
Do we measure fundamental frequency, intensity, or something else [@stevens2000]?

@@

As outlined in Section [Operationalizing speech](#s:operspeech), researchers are faced with a large amount of analytic choices when analyzing a multidimensional signal such as speech.
Analysts must identify and operationalize relevant measurements, as well as the temporal domain(s) from which these measurements are to be taken, and then possibly transform said measurements before submitting them to statistical models, which must be chosen alongside inferential criteria.
The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytic flexibility that social science might face across disciplines.
We will employed a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) how analytic and researcher-related predictors affect the final results.

In this study, we followed the procedures proposed by @Parker2020 and @aczel2021.
The project involved the following five phases:

@@

We have initially estimated that this process, from the time of an in-principle acceptance of the Stage 1 Registered Report to the end of Phase 5, would have taken nine months.
<!-- The factor most likely to delay our time-line is the rate of completion of the original set of analyses by independent analysis teams. -->
Phase 4. (meta-analysis) took longer than initially thought and the total duration of the project ended up lasting 12 months.

@@

As outlined above, our primary aim is to assess the variability of the reported effects, rather than the meta-analytic estimate of the investigated effect *per se*.
To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variability extracted from @silberzahn2018many.
The code is available at <https://many-speech-analyses.github.io/suppl/simulations.html>, Section 2.^[Cached model outputs can be found at <https://bit.ly/3AgdHAN>.]
Variability among teams was operationalized as the standard deviation of the teams' reported effects from @silberzahn2018many (which we *z*-scored prior to simulations to make it comparable to our study).
For the mean of the teams' true standard deviation (0.68 *z*-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams. 
Thus in order to achieve our main goal, i.e. estimating variability among teams, we considered a minimum sample size of 10 teams as sufficient.
Given the exploratory nature of our study, however, we have sampled as many analysts as possible.
We received initial expression of interest to participate from more than 200 analysts, although there has been a substantial drop-out rate (see Section Results).

@@

Each analysis was evaluated by four different analysts teams who functioned as peer-reviewers.
Each peer-reviewer was randomly assigned to analyses from at least four analysis teams.
Reviewers evaluated the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
The sequences was systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.

@@

The reviewers were also given the option to include further comments in a text box for each of the three ratings.

After submitting the review, a methods section from a second analysis was then made available to the reviewer.
This same sequence was followed until all analyses allocated to a given reviewer were provided and reviewed.^[We initially planned to simultaneously present all four (or more) methods sections to each reviewer after the fourth round, with the option to revise their original ratings and provide an explanation. We have decided to skip this last step due to time constrains.]

@@

The initiating authors (SC, JC, TR) conducted the analyses outlined in this section.
We did not conduct confirmatory tests of any *a priori* hypotheses.
We consider our analysis exploratory.

@@

After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported model, we conducted a \textsc{Bayesian random-effects meta-analysis} using a multi-level (intercept-only) regression model.
The outcome variable was the set of standardized effect sizes $\eta_i$.
The likelihood of $\eta_i$ was assumed to correspond to a normal distribution [@knight2000].
The analysis teams were entered as a group-level effect (i.e., `(1 | team)`, called *random effect* in the frequentist literature).
The standard errors $\text{se}_i$ were included as the standard deviation of $\eta_i$ to fit a measurement-error model, as discussed above.
We used regularizing weakly-informative priors for the intercept $\alpha$ ($Normal(0, 1)$) and for the group-level standard deviation $\sigma_{\alpha_{\text{t}}}$ ($HalfCauchy(0, 1)$).
We fitted this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan [@stan2021], and 4000 iterations (2000 for warm-up) per chain, distributed across 8 processing cores and 2 threads in within-chain parallelization.
<!-- In case of divergent transitions, we will increase `adapt_delta`, `tree_depth`, and the number of iterations in this order until we obtain a model fit with no divergent transitions. -->
The model did not incur in divergent transitions ($\hat{R}$ was equal or lower than 1) and the estimated sample sizes were sufficient.
<!-- TODO: add link to meta-model code -->
The code used to run the model can be found at <>.

@@

$$\text{SDI} = \frac{2|X \cap Y|}{|X|+|Y|}$$

where $|X \cap Y|$ is the number of variables common to both models in the pair, and $|X|+|Y|$ is the sum of the number of variables that occur in each model.

@@

In order to generate a unique SDI for each analysis team, we calculated the average of all pairwise SDIs for all pairs of analyses using the `beta.pair()` function in the betapart R package [@baselga2020].

@@

A normal distribution was used as the likelihood function of $\alpha_{t[i]}$.
The mean of $\alpha_{t[i]}$ was modeled on the basis of the overall intercept $\beta$ and on the coefficients of each predictor.
The numeric predictors were centered and scaled and the categorical predictors were sum coded.
As the prior for the intercept and the predictors we used a normal distribution with mean 0 and standard deviation 1.
The model was run with the same settings as with the meta-analytic model.
<!-- TODO: add link to predictor model code -->
The code used to run the model can be found at <LINK>.

@@

All relevant data, code, and materials have been publicly archived on the Open Science Framework (<https://osf.io/3bmcp/>).
Archived data includea the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyzed with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts.
Similarly, we archived both the analysis code used for each individual analysis and the code from our meta-analyses.
We also archived copies of our survey instruments from analysts and peer-reviewers.

We have exclude from our synthesis any individual analysis submitted after we have completed peer review or those unaccompanied by analysis files that allow us to understand what the analysts did.
We also excluded any individual analysis that does not produce an outcome that can be interpreted as an answer to our primary question.
<!-- TODO: mention that there were some and add info in descriptive stats section? -->

@@

The results section is divided into three parts.
We first provide a statistical description of team composition, nature of acoustic analyses and statistical approaches, and peer-review ratings.
Second, we report the results of the meta-analytic model, focusing on between-team variability and the estimated meta-analytic effect of word combination typicality on speech acoustics.
Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
The research compendium of study containing all the code and data presented here and can be found at <https://osf.io/3bmcp/>.

@@

`r pull_from_tib(team_desc_df, stage, "Submitted", n_teams) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` teams submitted their analyses by the established deadline. 
The analyses from which it was possible to extract an effect size were included in the meta-analysis. 
Of the submitted analyses, the initiating authors identified `r nrow(msa_models)` from `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams that were deemed eligible to be included in this study. 
In what follows, we describe the characteristics of these teams and analyses, i.e., those included in the meta-analyses. 
A complete summary of all the analyses from the `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` submitting teams is available in the supplementary materials.

The included analyses were provided by `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams, comprising `r pull_from_tib(team_desc_df, stage, "Final", n_analysts)` analysts, with an average of `r pull_from_tib(tbl_team_desc, label, "team_desc_size", avg)` (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_size", sd)`) individuals per team.
Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the data being released to the teams.
Analysts had on average `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", avg)` years (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", sd)`) of experience after completing their PhD, ranging from `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Min.)` years, i.e. PhD students (or younger) to `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Max)` years, suggesting that, on average, analyst were experienced researchers.
The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Min.)` to `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Max)` with an average of `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", avg)` (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", sd)`).
We take this to suggest that analysts had an overall rather high positive prior belief in the investigated relationship between acoustics and word combination typicality.

At the end of Phase 2 (primary data analysis), the teams have submitted a grand total `r no_analyses` individual models to answer the research question, with a mean of `r pull_from_tib(tbl_model_desc, label, "model_desc_models", avg)` (SD: `r pull_from_tib(tbl_model_desc, label, "model_desc_models", sd)`) models per team. 
Table \@ref(tab:descriptives-table) provides a summary of the contributing teams and their analyses. 
Crucially, the analytic approaches employed by the teams varied widely both in the acoustical analyses of the speech signal and in the statistical analyses of the obtained measures.
We proceed to discuss these in the following sections, after which we provide an overview of the peer-review ratings.

@@

The analytic teams differed in their approach to the acoustic analysis of the speech signal, including choices related to specific acoustic measures, the temporal window over which they are taken from and how the measures are transformed. 
`r round(outcome_n[[1,1]],2) * 100`\% of models used a measure of duration as the outcome variable, `r round(outcome_n[[2,1]],2) * 100`\% used fundamental frequency (f0), `r round(outcome_n[[3,1]],2) * 100`\% used vowel formants, `r round(outcome_n[[4,1]],2) * 100`\% intensity, and `r round(outcome_n[[5,1]],2) * 100`\% other measures.

@@

The majority of models were run within a frequentist framework (`r round(framework_n[[2,1]],2) * 100`\%).
`r round(framework_n[[1,1]],2) * 100`\% were run within a Bayesian framework.
While teams almost exclusively used linear models to analyze their data (`r round(model_n[[2,1]],2) * 100`\%), teams differed drastically in how they accounted for dependencies within the data.
<!-- TODO: The calculations in these sections are based on the INCLUDED models only. We are not counting the SUBMITTED models that have been excluded. We might want to add counts for when including the excluded models -->

>>>>

In this article, we investigate the impact of analytic choices on research results when many analyst teams examine the same speech production data set, a process that involves both decisions regarding the *operationalization* of a complex signal and decisions regarding *statistical analysis*.
Specifically, we discuss the degree of variability in research results obtained by 30 teams who had to choose the operationalization and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
Our goals are twofold: (i) our study conceptually replicates previous many-analyses projects, by probing the effects of different statistical analyses and by assessing the generalizability of published findings to other disciplines (here, the speech sciences);
(ii) our study extends the scope of inquiry to include flexibility in the operationalization of complex human behavior (here, human speech).
This is an important addition in that the increased number of "forking paths" in the "garden of analytic choices"---derived from the many decisions involved in quantification---might reveal a higher degree of variability across analysts than what previously observed, thus giving us a more realistic estimate of variability across analysts.

@@

Consequently, a good part of published papers likely present overconfident interpretations of data and statistical results based on idiosyncratic analytic strategies [e.g., @simmons2011false; @gelman2014statistical].
These interpretations, and the conclusions that derive from them, are thus associated with an unknown degree of uncertainty (dependent on the strength of evidence provided) and with an unknown degree of generalizability (dependent on the chosen analysis).
Moreover, the same data could lead to very different conclusions depending on the analytic path taken by the researcher.
However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
Despite recent efforts to improve transparency and reproducibility [e.g. @miguel2014promoting; @klein2018practical] and the advent of freely available and accessible infrastructures, such as those provided by the Open Science Framework ([osf.io](https://osf.io)), critical re-analyses of published analytic strategies are still uncommon because data sharing remains rare [@wicherts2006poor].

@@

Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
In a seminal collaborative effort, @silberzahn2018many let twenty-nine independent analysis teams address the same research hypothesis.
The analytic approaches and, consequently, the results varied widely between teams.
Sixty-nine percent of the teams found support for the hypothesis, and 31% did not.
Out of the 29 analytic strategies, there were 21 unique combinations of covariates.
Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses. 
The authors results suggest that analytic plurality may be an inevitable byproduct of the scientific process and not necessarily driven by different levels of expertise or bias.

Several other recent studies corroborated this analytic flexibility across different disciplines.
@dutilh2019 and @starns2019assessing investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams [see also @Parker2020, and @botvinik-nezer2020, regarding analytic flexibility in ecology and neuroimaging data, respectively].
@bastiaansen2020 crowdsourced clinical recommendations based on analyses of an individual patient.
Their results suggests that analysts differed substantially regarding decisions related to both the statistical analysis of the data and the theoretical rationale behind interpreting the statistical results.

Extending on the many-analysts approach, @landy2020crowdsourcing asked 15 research teams to independently design studies to answer the same research questions.
Again, they found vast heterogeneity in researchers' conclusions which was not predicted by the researchers' expertise, but rather seem to be more dependent on the research question itself.
This is in line with a recent re-analysis of @silberzahn2018many by @auspurg2021has.
The authors argue that the observed heterogeneity across analysts in @silberzahn2018many might have been driven by flexibility in statistically interpreting the research question.

While these studies attested a large degree of analytic flexibility with possibly impactful consequences, they focused on analytic decisions related to statistical inference or the architecture of computational models. 
In these studies the data sets were fixed and neither data collection nor measurement could be changed.
Thus the estimates of variability found in the literature might reflect a lower bound only, ignoring large parts of the forking paths related to measurement. 
However, in many fields the primary raw data are complex signals that need to be operationalized relative to a theoretically motivated research question.
This is especially true in the social sciences, where the phenomenon under investigation corresponds to both observable and unobservable human behavior.

@@

\noindent Depending on the speaker's intention, this sentence can be said in different ways.
For instance, if the speaker is exhausted by all their meetings, they might acoustically highlight the word *another* or *meeting* to contrast it with more pleasant activities.
If, on the other hand, the speaker is just tired of video conferences, as opposed to say face-to-face meetings, they might acoustically highlight the word *Zoom*.

@@

From a phonetic viewpoint, linguistically relevant units are inherently multidimensional and dynamic: they consist of clusters of parameters that are modulated over time.
The acoustic parameters of units are usually asynchronous, i.e. they appear at different time points in the unfolding signal, and overlap with parameters of other units [e.g. @jongman2000acoustic; @lisker1986voicing; @summerfield1981articulatory; @winter2014spoken].
A classical example is the distinction between voiced and voiceless stops in English (i.e. /b/ and /p/ in *bear* vs. *pear*).
This contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds [@lisker1977rapid].
Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
For example, the initial /l/ of the English words *led* and *let* is affected by the voicing of the final consonant (/d, t/) [@hawkins2004influence].

The multiplicity of phonetic measurements grows exponentially if we look at larger temporal domains, as is the case with suprasegmental aspects of speech.
For example, studies investigating acoustic correlates of word stress (e.g. the difference between *ínsight* and *incíte*) use a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) [e.g., @gordon2017acoustic].
Moving on to the expression of higher-level communicative functions, like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances [e.g., @ladd2008intonational].
Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions [e.g., @niebuhr2011].
The latter can also be expressed by global vs. local pitch modulations [@heuven2002], as well as acoustic information within the temporal or spectral domain [e.g., @van2005speech].
Extra-linguistic information, like the speaker's intentions, levels of emotional arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch [@foulkes2006; @ogden2004; @white2009].

In short, when testing hypotheses on speakers' intentions with speech production data, researchers are faced with many choices and possibilities.
The larger the functional domain (e.g. segments vs. words vs. utterances), the higher the number of conceivable operationalizations.
For example, several decisions have to be made when comparing the two realizations of the sentence in (1), one of which is intended to signal emphasis on *another* and one of which emphasizes *Zoom* (see 2a and 2b).

@@

\noindent Do we compare only the word *another* in (2a) and (2b), or also the word *Zoom*?
Do we measure utterance-wide acoustic profiles, whole words, or just stressed syllables?
Do we average across the chosen time domain or do we measure a specific point in time?
Do we measure fundamental frequency, intensity, or something else [@stevens2000]?

@@

As outlined in Section [Operationalizing speech](#s:operspeech), researchers are faced with a large amount of analytic choices when analyzing a multidimensional signal such as speech.
Analysts must identify and operationalize relevant measurements, as well as the temporal domain(s) from which these measurements are to be taken, and then possibly transform said measurements before submitting them to statistical models, which must be chosen alongside inferential criteria.
The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytic flexibility that social science might face across disciplines.
We employed a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) how analytic and researcher-related predictors affect the final results.

In this study, we followed the procedures proposed by @Parker2020 and @aczel2021.
The project comprised the following five phases:

@@

We initially estimated that this process, from the time of an in-principle acceptance of the Stage 1 Registered Report to the end of Phase 5, would take nine months.
<!-- The factor most likely to delay our time-line is the rate of completion of the original set of analyses by independent analysis teams. -->
Phase 4 (meta-analysis) took longer than initially anticipated and the total duration of the project was approximately 12 months.

@@

As outlined above, our primary aim is to assess the variability of the reported effects, rather than the meta-analytic estimate of the investigated effect *per se*.
To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variability extracted from @silberzahn2018many.
The code is available at <https://many-speech-analyses.github.io/suppl/simulations.html>, Section 2.^[Cached model outputs can be found at <https://bit.ly/3AgdHAN>.]
Variability among teams was operationalized as the standard deviation of the teams' reported effects from @silberzahn2018many (which we *z*-scored prior to simulations to make it comparable to our study).
For the mean of the teams' true standard deviation (0.68 *z*-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams. 
Thus in order to achieve our main goal, i.e. estimating variability among teams, we considered a minimum sample size of 10 teams as sufficient.
Given the exploratory nature of our study, however, we have sampled as many analysts as possible.
We received initial expression of interest to participate from more than 200 analysts, though there was a substantial drop-out rate (see Section Results).

@@

Each analysis was evaluated by four different analysts teams who functioned as peer-reviewers.
Each peer-reviewer was randomly assigned to analyses from at least four analysis teams.
Reviewers evaluated the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
The sequences were systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.

@@

\noindent The reviewers were also given the option to include further comments in a text box for each of the three ratings.

After submitting the review, a methods section from a second analysis was then made available to the reviewer.
This same sequence was followed until all analyses allocated to a given reviewer were provided and reviewed.^[Initially we planned to present simultaneously all four (or more) methods sections to each reviewer after the fourth round, with the option to revise their original ratings and provide an explanation. Ultimately, we decided to skip this step due to time constraints.]

@@

The initiating authors (SC, JC, TR) conducted the analyses outlined in this section.
We did not conduct confirmatory tests of any *a priori* hypotheses.
We consider our analyses exploratory.

@@

After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported model, we conducted a \textsc{Bayesian random-effects meta-analysis} using a multi-level (intercept-only) regression model.
The outcome variable was the set of standardized effect sizes $\eta_i$.
The likelihood of $\eta_i$ was assumed to correspond to a normal distribution [@knight2000].
The analysis teams were entered as a group-level effect (i.e., `(1 | team)`, called *random effect* in the frequentist literature).
The standard errors $\text{se}_i$ were included as the standard deviation of $\eta_i$ to fit a measurement-error model, as discussed above.
We used regularizing weakly-informative priors for the intercept $\alpha$ ($Normal(0, 1)$) and for the group-level standard deviation $\sigma_{\alpha_{\text{t}}}$ ($HalfCauchy(0, 1)$).
We fitted this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan [@stan2021], and 4000 iterations (2000 for warm-up) per chain, distributed across 8 processing cores and 2 threads in within-chain parallelization.
<!-- In case of divergent transitions, we will increase `adapt_delta`, `tree_depth`, and the number of iterations in this order until we obtain a model fit with no divergent transitions. -->
The model did not incur any divergent transitions ($\hat{R}$ was equal or lower than 1) and the estimated sample sizes were sufficient.
<!-- TODO: add link to meta-model code -->
The code used to run the model can be found at <>.

@@

$$\text{SDI} = \frac{2|X \cap Y|}{|X|+|Y|}$$
\vspace{0.05in}

@@

\noindent where $|X \cap Y|$ is the number of variables common to both models in the pair, and $|X|+|Y|$ is the sum of the number of variables that occur in each model.
In order to generate a unique SDI for each analysis team, we calculated the average of all pairwise SDIs for all pairs of analyses using the `beta.pair()` function in the betapart R package [@baselga2020].

@@

A normal distribution was used as the likelihood function of $\alpha_{t[i]}$.
The mean of $\alpha_{t[i]}$ was modeled on the basis of the overall intercept $\beta$ and on the coefficients of each predictor.
The numeric predictors were centered and scaled and the categorical predictors were sum coded.
We used a normal distribution with mean 0 and standard deviation 1 as the prior for the intercept and the predictors.
The model was run with the same settings as with the meta-analytic model.
<!-- TODO: add link to predictor model code -->
The code used to run the model can be found at <LINK>.

@@

All relevant data, code, and materials have been publicly archived on the Open Science Framework (<https://osf.io/3bmcp/>).
Archived data include the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyzed with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts.
Similarly, we archived both the analysis code used for each individual analysis and the code from our meta-analyses.
We also archived copies of our survey instruments from analysts and peer-reviewers.

We excluded from our synthesis any individual analysis submitted after peer review (Phase 3) or those unaccompanied by analysis files without which it was not possible to understand what the analysts did.
We also excluded any individual analysis that does not produce an outcome that can be interpreted as an answer to our primary question.
<!-- TODO: mention that there were some and add info in descriptive stats section? -->

@@

The results section is divided into three parts.
We first provide a statistical description of team composition, nature of acoustic analyses and statistical approaches, and peer-review ratings.
Second, we report the results of the meta-analytic model, focusing on between-team variability and the estimated meta-analytic effect of word combination typicality on speech acoustics.
Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
The research compendium of the study containing all the code and data presented here and can be found at <https://osf.io/3bmcp/>.

@@

`r pull_from_tib(team_desc_df, stage, "Submitted", n_teams) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` teams submitted their analyses by the established deadline. 
The analyses from which it was possible to extract an effect size were included in the meta-analysis. 
Of the submitted analyses, the initiating authors identified `r nrow(msa_models)` from `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams that were deemed eligible to be included in the meta-analytic synthesis. 
In what follows, we describe the characteristics of these teams and analyses. 
A complete summary of all the analyses from the `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` submitting teams is available in the supplementary materials.

The included analyses were provided by `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams, comprising `r pull_from_tib(team_desc_df, stage, "Final", n_analysts)` analysts, with an average of `r pull_from_tib(tbl_team_desc, label, "team_desc_size", avg)` (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_size", sd)`) individuals per team.
Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the data being released to the teams.
Analysts had on average `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", avg)` years (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", sd)`) of experience after completing their PhD, ranging from `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Min.)` years, i.e. PhD students (or younger) to `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Max)` years, suggesting that, on average, analyst were experienced researchers.
The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Min.)` to `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Max)` with an average of `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", avg)` (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", sd)`).
We take this to suggest that, overall, analysts had a rather high positive prior belief in the investigated relationship between acoustics and word combination typicality.

At the end of Phase 2 (primary data analysis), the teams had submitted a grand total `r no_analyses` individual models to answer the research question, with a mean of `r pull_from_tib(tbl_model_desc, label, "model_desc_models", avg)` (SD: `r pull_from_tib(tbl_model_desc, label, "model_desc_models", sd)`) models per team. 
Table \@ref(tab:descriptives-table) provides a summary of the contributing teams and their analyses. 
Crucially, the analytic approaches employed by the teams varied widely both in the acoustical analyses of the speech signal and in the statistical analyses of the obtained measures.
We proceed to discuss these in the following sections, after which we provide an overview of the peer-review ratings.

@@

The analytic teams differed in their approach to the acoustic analysis of the speech signal, including choices related to specific acoustic measures, the temporal window over which they are taken from and how the measures are transformed. 
`r (round(outcome_n[[1,1]],2) * 100) %>% xfun::numbers_to_words() %>% str_to_sentence()` percent of the models used a measure of duration as the outcome variable, `r round(outcome_n[[2,1]],2) * 100`\% used fundamental frequency (f0), `r round(outcome_n[[3,1]],2) * 100`\% used vowel formants, `r round(outcome_n[[4,1]],2) * 100`\% intensity, and `r round(outcome_n[[5,1]],2) * 100`\% other measures.

@@

The majority of models were run within a frequentist framework (`r round(framework_n[[2,1]],2) * 100`\%).
`r (round(framework_n[[1,1]],2) * 100) %>% xfun::numbers_to_words() %>% str_to_sentence()` percent were run within a Bayesian framework.
While teams almost exclusively used linear models to analyze their data (`r round(model_n[[2,1]],2) * 100`\%), teams differed drastically in how they accounted for dependencies within the data.
<!-- TODO: The calculations in these sections are based on the INCLUDED models only. We are not counting the SUBMITTED models that have been excluded. We might want to add counts for when including the excluded models -->
